Capstone Movielens Report

### 2025-05-11 reports/capstone-movielens-report.draft4.Rmd
Draft report development: `` parameter of the `model.tune.param_range` function described.

###### Parameters
\
####### loop_starter 
\
A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval on which the parameter value that minimizes `RMSE` is sought.
`dvs` is a divisor for splitting the interval to transform it into a sequence of values among which the value that minimizes `RMSE` is sought.
For this purpose, the sequence step is calculated as follows:
$$
step = \frac{end - start}{dvs}
$$

@@

####### tune_dir_path 
\

To improve performance, the algorithm caches intermediate results in the file system. This parameter specifies the path to the directory where the cache files are saved.

####### cache_file_base_name 
\

The algorithm generates unique names for cache files based on this and the `loop_starter` parameter, as well as some other intermediate values calculated during the execution.

#######  fn_tune.test.param_value
\

This is a helper function name that is passed to the same-named parameter of the [tune.model_param] function that is called internally during the execution (see the [description of the `tune.model_param` function](#func.tune.model_param) above).

  - **max.identical.min_RMSE.count:** ;

>>>>

####### loop_starter 
\
A numeric vector of the form `c(start, end, dvs)`, where `start` and `end` are the endpoints of the interval on which the parameter value that minimizes `RMSE` is sought.
`dvs` is a divisor for splitting the interval to transform it into a sequence of values among which the value that minimizes `RMSE` is sought.
For this purpose, the sequence step is calculated as follows:
$$
step = \frac{end - start}{dvs}
$$

@@

####### tune_dir_path 
\
To improve performance, the algorithm caches intermediate results in the file system. This parameter specifies the path to the directory where the files are cached.

####### cache_file_base_name 
\
The algorithm generates unique names for cache files based on this and the `loop_starter` parameter, as well as some other intermediate values calculated during the execution.

#######  fn_tune.test.param_value
\
This is a helper function name that is passed to the same-named parameter of the [tune.model_param](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L116) function that is called internally during the execution (see the description of the `tune.model_param` function [above](#func.tune.model_param)).

####### max.identical.min_RMSE.count
\
If more than one identical minimum `RMSE` value is calculated during execution, the number of identical minimums is limited by the value of this parameter. When it is reached, the algorithm considers the task execution to be complete.

### 2025-05-11 reports/capstone-movielens-report.draft4.tex
Draft report development: `` parameter of the `model.tune.param_range` function described.

\hfill\break
\#\#\#\#\#\#\# loop\_starter\\

A numeric vector of the form \texttt{c(start,\ end,\ dvs)}, where
\texttt{start} and \texttt{end} are the endpoints of the interval on
which the parameter value that minimizes \texttt{RMSE} is sought.
\texttt{dvs} is a divisor for splitting the interval to transform it
into a sequence of values among which the value that minimizes
\texttt{RMSE} is sought. For this purpose, the sequence step is
calculated as follows: \[
step = \frac{end - start}{dvs}
\]

@@

To improve performance, the algorithm caches intermediate results in the
file system. This parameter specifies the path to the directory where
the files are cached.

@@

The algorithm generates unique names for cache files based on this and
the \texttt{loop\_starter} parameter, as well as some other intermediate
values calculated during the execution.

@@

This is a helper function name that is passed to the same-named
parameter of the
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L116}{tune.model\_param}
function that is called internally during the execution (see the
description of the \texttt{tune.model\_param} function
\hyperref[func.tune.model_param]{above}).

\begin{itemize}
\tightlist
\item
  \textbf{max.identical.min\_RMSE.count:} ;
\end{itemize}

>>>>

loop\_starter

\hfill\break
A numeric vector of the form \texttt{c(start,\ end,\ dvs)}, where
\texttt{start} and \texttt{end} are the endpoints of the interval on
which the parameter value that minimizes \texttt{RMSE} is sought.
\texttt{dvs} is a divisor for splitting the interval to transform it
into a sequence of values among which the value that minimizes
\texttt{RMSE} is sought. For this purpose, the sequence step is
calculated as follows: \[
step = \frac{end - start}{dvs}
\]

@@

\hfill\break
To improve performance, the algorithm caches intermediate results in the
file system. This parameter specifies the path to the directory where
the files are cached.

@@

\hfill\break
The algorithm generates unique names for cache files based on this and
the \texttt{loop\_starter} parameter, as well as some other intermediate
values calculated during the execution.

@@

\hfill\break
This is a helper function name that is passed to the same-named
parameter of the
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R\#L116}{tune.model\_param}
function that is called internally during the execution (see the
description of the \texttt{tune.model\_param} function
\hyperref[func.tune.model_param]{above}).

max.identical.min\_RMSE.count

\hfill\break
If more than one identical minimum \texttt{RMSE} value is calculated
during execution, the number of identical minimums is limited by the
value of this parameter. When it is reached, the algorithm considers the
task execution to be complete.
